Cognitive and Auditory Predictors of Dysarthric Speech Understanding in Older

### 2023-12-23 Manuscript Analyses/manuscript_analysis.Rmd
scripting elastic net models - wip

# Loading in needed packages
library(tidyverse) #install.packages("tidyverse")
library(rio) #install.packages("rio")
library(gt) #install.packages("gt")
library(gtsummary) #install.packages("gtsummary")
library(reshape2) #install.packages("reshape2")
library(ggcorrplot) #install.packages("ggcorrplot")
library(patchwork) #install.packages("patchwork")
library(janitor) #install.packages("janitor")
library(fs) #install.packages("fs")
library(furniture) #install.packages("furniture")
library(caret) #install.packages("caret")
library(effectsize) #install.packages("effectsize")
library(parameters) #install.packages("parameters")
library(performance) #install.packages("performance")
library(bayestestR) #install.packages("bayestestR)
library(rstanarm) #install.packages("rstanarm")
library(afex) #install.packages("afex")

# Load in dataset

demo <- rio::import("participant_demo.csv")

data <- rio::import("cleaned_data.csv")

## Function for model training
training <- function(data, method, int) {
  form = if (isTRUE(int)) {
    d2 = model.matrix(pwc ~ . * ., data = data)[, -1] %>%
      as_tibble() %>%
      janitor::clean_names()
    d2$pwc = data$pwc
  } else {
    d2 = data
    train(
      pwc ~.,
      data = d2,
      preProcess = c("center", "scale"),
      method = "repeatedcv",
      number = 5,
      repeats = 10
    )
  }
}

@@

# removing unneeded objects from the environment
rm(age)

@@

## Pre-Post Change

@@

@@

### Cognition

@@

>>>>

# Loading in needed packages
library(tidyverse) #install.packages("tidyverse")
library(rio) #install.packages("rio")
library(gt) #install.packages("gt")
library(gtsummary) #install.packages("gtsummary")
library(reshape2) #install.packages("reshape2")
library(ggcorrplot) #install.packages("ggcorrplot")
library(patchwork) #install.packages("patchwork")
library(janitor) #install.packages("janitor")
library(fs) #install.packages("fs")
library(furniture) #install.packages("furniture")
library(caret) #install.packages("caret")
library(effectsize) #install.packages("effectsize")
library(parameters) #install.packages("parameters")
library(performance) #install.packages("performance")
library(bayestestR) #install.packages("bayestestR)
library(rstanarm) #install.packages("rstanarm")
library(afex) #install.packages("afex")
library(glmnet) #install.packages("glmnet")

# Load in datasets

## Listener Demographic Information
demo <- rio::import("participant_demo.csv")

## Listener Intelligibility and Cognition Scores
data <- rio::import("cleaned_data.csv")

@@

# removing unneeded objects from the environment
rm(age, data)

@@

@@

## Function for model training
training <- function(data, method, int) {
  form = if (isTRUE(int)) {
    d2 = model.matrix(mean_pwc ~ . * ., data = data)[, -1] %>%
      as_tibble() %>%
      janitor::clean_names()
    d2$mean_pwc = data$mean_pwc
  } else {
    d2 = data
    train(
      mean_pwc ~ ., 
      data = d2, 
      preProcess = c("center", "scale"),
      method = method, 
      trControl = caret::trainControl(
        method = "repeatedcv",
        number = 5,
        repeats = 10
    ))
  }
}

@@

@@

set.seed(7036)

mod_fun = function(speaker, type){
  subsetted = pl_int %>% 
    filter(type == {{type}}) %>% 
    filter(speaker == {{speaker}}) %>% 
    select(mean_pwc, ends_with("_c"), best_win) %>% 
    drop_na(mean_pwc, ends_with("_c"), best_win) %>% 
    select(-contains("fluid"))

  mod.1 = training(subsetted, "glmnet", int = FALSE)
  mod.2 = training(subsetted, "glmnet", int = TRUE)

  return(list(mod.1, mod.2))
}

plot_fun = function(mods, title){
  plot_importance(
    mods = mods,
    labels = c("main", "int")
  ) %>% 
    drop_na(value) %>% 
    mutate(name = factor(
      name, 
      levels = c("main", "int"),
      labels = c(
        paste0("Main Effects"),
        paste0("Interactions")
    ))) %>% 
    filter(name == "Interactions") %>% 
    mutate(var = str_replace(var, "flanker_c", "Inhibitory Control of Attention"),
           var = str_replace(var, "card_sort_c", "Cognitive Flexibility"),
           var = str_replace(var, "vocab_c", "Vocabulary Knowledge"),
           var = str_replace(var, "pattern_c", "Processing Speed"),
           var = str_replace(var, "list_sort_c", "Working Memory"),
           var = str_replace(var, "pic_seq_c", "Picture Sequence Memory"),
           var = str_replace(var, "best_win", "Words in Noise Threshold"),
           var = str_replace(var, "_", " x ")) %>% 
    arrange(value) %>% 
    mutate(var = fct_inorder(var)) %>% 
    ggplot(aes(x = value, y = var, color = value)) +
    geom_segment(aes(xend = 0, yend = var)) +
    geom_point(size = 2) +
    facet_wrap(~name, scales = "free") +
    labs(x = "Relative Importance",
         y = "",
         title = {{title}}) +
    scale_color_viridis_c(option = "magma", end = .8) +
    theme(plot.title.position = "plot")
}

mods1 = mod_fun("AM1", "pretest")
mods2 = mod_fun("PDM10", "pretest")

p1 = plot_fun(mods1, "a) Ataxic")
p2 = plot_fun(mods2, "b) PD")
